Case study validations of automatic bullet matching\tnoteref{t1}\tnoteref{t2}

### 2019-11-10 index.Rnw
Add CMS to the comparison of scores figures

<<compare, fig.width = 8, fig.height = 5, fig.cap="Density curves of similarity scores from cross correlation (top) and RF scores (bottom). Different colors indicate same source versus different source. Ideally all scores of different source pairs should be much lower than scores for same source pairs.">>=
nests <- rbind(
  h44nest %>%
    select(sam_rf, sam_ccf, samesource) %>%
    mutate(study = "Hamby 44", group1 = NA),
  pdnest %>%
    select(sam_rf, sam_ccf, samesource) %>%
    mutate(study = "Phoenix PD", group1 = NA),
  hounest %>%
    select(sam_rf, sam_ccf,  samesource, group1) %>%
    mutate(study = "Houston FSI")
)
nests$study <- factor(nests$study, levels = c("Hamby 44", "Phoenix PD", "Houston FSI"))
nestslong <- nests %>% gather(key = "measure", value = "value", sam_rf, sam_ccf)
nestslong$measure <- factor(nestslong$measure)
levels(nestslong$measure) <- c("Cross correlation",  "RF score")

labels <- h44nest %>% filter(samesource, sam_rf < 0.5)
labels$comparison <- with(labels, paste(bullet1, "vs", paste(barrel2, bullet2, sep = "-")))
labels$measure <- "RF score"
labels$study <- "Hamby 44"
labels$y <- 5 + 4:1
nestslong %>%
  ggplot(aes(
    x = value, fill = samesource,
    colour = samesource
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.5, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("SAM scores", limits=c(0,1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F) +
  geom_text(aes(x = sam_rf, y = y, label = comparison),
            show.legend = F,
            hjust = 0,
            data = labels
  ) +
  geom_segment(aes(x = sam_rf, xend = sam_rf, y = 0, yend = y),
               show.legend = F,
               size = 0.1,
               colour = "grey20",
               data = labels
  )
@

@@

<<compare-land-to-land, fig.width = 8, fig.height = 4, fig.cap="Density curves of land-to-land similarity scores from cross correlation (top) and RF scores (bottom). Different colors indicate same source versus different source for each land. RF scores for different source comparisons are generally well below 0.5. Some same-source comparisons are also below 0.5 for RF scores, indicating potential problems with at least one of the lands involved in the comparison.">>=
all_lands %>% 
  gather(key = "measure", value = "value", ccf, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "rfscore"),
                          labels = c("Cross correlation", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
#  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F)
@

>>>>

<<compare, fig.width = 8, fig.height = 7, fig.cap="Density curves of similarity scores from random forest scores (top), cross correlation (middle), and consecutive matching striae (bottom). Different colors indicate same source versus different source. Ideally all scores of different source pairs should be much lower than scores for same source pairs.">>=
nests <- rbind(
  h44nest %>%
    select(sam_rf, sam_ccf, sam_cms, samesource) %>%
    mutate(study = "Hamby 44", group1 = NA),
  pdnest %>%
    select(sam_rf, sam_ccf, sam_cms, samesource) %>%
    mutate(study = "Phoenix PD", group1 = NA),
  hounest %>%
    select(sam_rf, sam_ccf, sam_cms, samesource, group1) %>%
    mutate(study = "Houston FSI")
)
nests$study <- factor(nests$study, levels = c("Hamby 44", "Phoenix PD", "Houston FSI"))
nestslong <- nests %>% gather(key = "measure", value = "value", sam_rf, sam_ccf, sam_cms)
nestslong$measure <- factor(nestslong$measure)
levels(nestslong$measure) <- c("Cross correlation", "CMS", "RF score")

labels <- h44nest %>% filter(samesource, sam_rf < 0.5)
labels$comparison <- with(labels, paste(bullet1, "vs", paste(barrel2, bullet2, sep = "-")))
labels$measure <- "RF score"
labels$study <- "Hamby 44"
labels$y <- 5 + 4:1
p1 <- nestslong %>%
  filter(measure %in% c("RF score")) %>%
  ggplot(aes(
    x = value, fill = samesource,
    colour = samesource
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.3, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_x_continuous("SAM scores", limits=c(0,1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F) +
  geom_text(aes(x = sam_rf, y = y, label = comparison),
            show.legend = F,
            hjust = 0,
            data = labels
  ) +
  geom_segment(aes(x = sam_rf, xend = sam_rf, y = 0, yend = y),
               show.legend = F,
               size = 0.1,
               colour = "grey20",
               data = labels
  ) + 
  theme(axis.title.x = element_blank(), axis.text.y = element_text(hjust = .5, angle = 90))

p2 <- nestslong %>%
  filter(measure %in% c("Cross correlation")) %>% 
  ggplot(aes(
    x = value, fill = samesource,
    colour = samesource
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.3, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  theme(legend.position = "bottom") +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_x_continuous("SAM scores") + 
  theme(axis.title.x = element_blank(), axis.text.y = element_text(hjust = .5, angle = 90))

p3 <- nestslong %>%
  filter(measure %in% c("CMS")) %>% 
  ggplot(aes(
    x = value, fill = samesource,
    colour = samesource
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(aes(x = jitter(value)), alpha = 0.3, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  theme(legend.position = "bottom") +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("SAM scores")  + 
  theme(axis.text.y = element_text(hjust = .5, angle = 90))

grid.arrange(p1, p2, p3, nrow = 3, heights = c(1, 1, 1.4))
@

@@

<<compare-land-to-land, fig.width = 8, fig.height = 6.5, fig.cap="Density curves of land-to-land similarity scores from RF scores (top), cross-correlation (middle), and consecutive matching striae (CMS)(bottom). Different colors indicate same source versus different source for each land. RF scores for different source comparisons are generally well below 0.5. Some same-source comparisons are also below 0.5 for RF scores, indicating potential problems with at least one of the lands involved in the comparison.">>=
# all_lands %>% 
#   gather(key = "measure", value = "value", ccf, rfscore) %>%
#   mutate(measure = factor(measure, levels = c("ccf", "rfscore"),
#                           labels = c("Cross correlation", "RF score")),
#          study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
#   ggplot(aes(
#     x = value, fill = sameland,
#     colour = sameland
#   )) +
#   geom_density(alpha = 0.6) +
# #  geom_rug(alpha = 0.5/12, show.legend = F) +
#   facet_grid(measure ~ study) +
#   theme_bw() +
#   scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
#   scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
#   scale_x_continuous("Land-to-Land scores", limits = c(0, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
#   theme(legend.position = "bottom") +
#   geom_hline(yintercept = 0, show.legend = F)
p1 <- all_lands %>% 
  gather(key = "measure", value = "value", ccf, cms, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "cms", "rfscore"),
                          labels = c("Cross correlation", "CMS", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  filter(measure == "RF score") %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
#  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme(legend.position = "bottom", axis.title.x = element_blank(), axis.text.y = element_text(hjust = .5, angle = 90)) +
  geom_hline(yintercept = 0, show.legend = F)

p2 <- all_lands %>% 
  gather(key = "measure", value = "value", ccf, cms, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "cms", "rfscore"),
                          labels = c("Cross correlation", "CMS", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  filter(measure == "Cross correlation") %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
#  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange"), guide = F) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1), labels = c(0, 0.25, 0.5, 0.75, 1)) +
  theme(legend.position = "bottom", axis.title.x = element_blank(), axis.text.y = element_text(hjust = .5, angle = 90)) +
  geom_hline(yintercept = 0, show.legend = F)

p3 <- all_lands %>% 
  gather(key = "measure", value = "value", ccf, cms, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "cms", "rfscore"),
                          labels = c("Cross correlation", "CMS", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  filter(measure == "CMS") %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
#  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores") +
  theme(legend.position = "bottom", axis.text.y = element_text(hjust = .5, angle = 90)) +
  geom_hline(yintercept = 0, show.legend = F)

grid.arrange(p1, p2, p3, nrow = 3, heights = c(1, 1, 1.4))
@
